---
title: "Index.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Scripts/Chart Script 1.R")
source("Scripts/Aggregate Table Script.R")
```

## Summary Information Script




## Aggregate Table Script
```{r table, echo = FALSE}
kable(summary_df, col.names = c("County", "Start of Week date",
                                "Confirmed Cases", "Ages 0-19", 
                                "Ages 20-34", "Ages 35-49", "Ages 50-64", 
                                "Ages 65-79", "Ages 80+"), align = "c")
```

We added this summarized table to show all the times when confirmed cases were above 2500 cases. With this, we broke it down by age group to let the audience see what group of people were more likely to get it. We were able to see that people ages 20-34 were more likely to get it compared to every other age group. Also with the weeks with over 2500 confirmed cases, we can see that King county was responsible for every one of those except for one, which was Spokane county.



## Chart Script 1
```{r plot, echo =  FALSE}
bar_plot
```

For our first chart script we chose to do it about what day is most common to get the vaccine. We chose to do it in a bar chart because it was a good way of seeing which day triumphs another. We included this as a way for the audience to see which days are the busiest according to our dataset and maybe they can avoid those days to reduce waiting times and potentially save them time. It seems that most days, there is about the same amount of people getting vaccinated each day of the week but Sunday seems to be slightly less than all the others.


##  Chart Script 2






##  Chart Script 3
