---
title: "Index.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Scripts/Chart Script 1.R")
source("Scripts/Aggregate Table Script.R")
source("Scripts/Chart Script 3.R")
```

## Introduction

We chose to do our topic on covid just because of how much it has impacted our lives this past year. We wanted to research how severe this disease actually is, at many stages throughout this time. As well as the future of covid with people now getting vaccinated and how the vaccine will affect us. We acquired multiple datasets from deaths across the world, vaccinations in the US, and cases in Washington.
## Summary Information Script




## Aggregate Table Script
```{r echo = FALSE, message = FALSE}
kable(summary_df(WA_df), col.names = c("County","Confirmed Cases", "Ages 0-19", 
                                "Ages 20-34", "Ages 35-49", "Ages 50-64", 
                                "Ages 65-79", "Ages 80+"), align = "c")
```

We added this summarized table to show the confirm cases in different county within Washington. With this, we broke it down by age group to let the audience see what group of people were more likely to get it. From the table, we were able to identify that King County contain the highest amount of confirm cases. We were able to also see that people ages 20-34 were more likely to get it compared to every other age group (a common trend in almost every county). Surprisingly the Columbia contain the least amount of confirmed cases. Another common trend that we can see from the table is that the ages 80+ group are the least to get covid-19. This is most likely due to because young adult still goes out normally while elders are more likely to stay home. 



## Chart Script 1
```{r plot, echo =  FALSE}
bar_graph
```

For our first chart script we chose to do it about what day is most common to get the vaccine. We chose to do it in a bar chart because it was a good way of seeing which day triumphs another. We included this as a way for the audience to see which days are the busiest according to our dataset and maybe they can avoid those days to reduce waiting times and potentially save them time. It seems that most days, there is about the same amount of people getting vaccinated each day of the week but Sunday seems to be slightly less than all the others.


##  Chart Script 2






##  Chart Script 3

